Multi-resolution Neural Field Estimation

### 2011-03-04 Multiresolution_framework/ltx/manuscript.tex
minor edit

The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as fluid dynamics, weather systems, ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}. \parham{Mike,Ken: can add to this list?}

>>>>

The MRAIDE approach is not limited to neural fields, where the framework can be applied modeling other multi-resolution spatiotemporal dynamical systems such as weather systems and ecological systems, and others\cite{Wikle2002,Xu2005,Fort2008}. \parham{Mike,Ken: can add to this list?}
